---
title: "Untitled"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
human_all <- as.list(read.csv("~/Downloads/entrez/human_all_entrez.txt", header = F))$V1
human_conserved <- as.list(read.csv("~/Downloads/entrez/human_conserved_entrez.txt", header = F))$V1
human_specific <- as.list(read.csv("~/Downloads/entrez/human_specific_entrez.txt", header = F))$V1

yeast_all <- as.list(read.csv("~/Downloads/entrez/yeast_all_entrez.txt", header = F))$V1
yeast_conserved <- as.list(read.csv("~/Downloads/entrez/yeast_conserved_entrez.txt", header = F))$V1
yeast_specific <- as.list(read.csv("~/Downloads/entrez/yeast_specific_entrez.txt", header = F))$V1

library(org.Hs.eg.db)
library(org.Sc.sgd.db)
library(enrichplot)
library(clusterProfiler)
library(GOSemSim)
library(clusterProfiler)
library(stringr)
library(ggplot2)

```



# mgeneSim(genes, semData=hsGO2, measure="Wang", combine="BMA", verbose=FALSE)
#mgeneSim(genes, semData=hsGO2, measure="Wang", combine="BMA", verbose=FALSE)

#mclusterSim(list(a=human_conserved, b=human_specific),
#            semData=godata('org.Hs.eg.db', ont="MF"), 
#            measure="Jiang", combine="BMA")
#mclusterSim(list(a=human_conserved, b=human_specific),
#            semData=godata('org.Hs.eg.db', ont="BP"), 
#            measure="Jiang", combine="BMA")
#mclusterSim(list(a=human_conserved, b=human_specific),
#            semData=godata('org.Hs.eg.db', ont="CC"), 
#            measure="Jiang", combine="BMA")

#mclusterSim(list(a=yeast_conserved, b=yeast_specific),
#            semData=godata('org.Sc.sgd.db', ont="MF"), 
#            measure="Jiang", combine="BMA")
#mclusterSim(list(a=human_conserved, b=yeast_specific),
#            semData=godata('org.Sc.sgd.db', ont="BP"), 
#            measure="Jiang", combine="BMA")
#mclusterSim(list(a=human_conserved, b=yeast_specific),
#            semData=godata('org.Sc.sgd.db', ont="CC"), 
#            measure="Jiang", combine="BMA")

# GO Over-representation Analysis



```{r}
human_specific_ego <- enrichGO(gene = human_specific, 
                               universe = names(human_all),
                               OrgDb = org.Hs.eg.db,
                               ont           = "ALL",
                               pAdjustMethod = "fdr",
                               pvalueCutoff  = 0.01,
                               qvalueCutoff  = 0.05)
head(human_specific_ego)
```


```{r}
human_conserved_ego <- enrichGO(gene = human_conserved, 
                                universe = names(human_all),
                                OrgDb = org.Hs.eg.db,
                                ont = "ALL",
                                pAdjustMethod = "fdr",
                                pvalueCutoff  = 0.01,
                                qvalueCutoff  = 0.05)
head(human_conserved_ego)

```

dim(human_conserved_ego)
dim(human_specific_ego)
dim(yeast_conserved_ego)
dim(yeast_specific_ego)

```{r}
yeast_specific_ego <- enrichGO(gene = yeast_specific, 
                               universe = names(yeast_all),
                               OrgDb = org.Sc.sgd.db,
                               ont = "ALL",
                               pAdjustMethod = "fdr",
                               pvalueCutoff  = 0.01,
                               qvalueCutoff  = 0.05)
head(human_specific_ego)
```


human_specific_ego

```{r}
yeast_conserved_ego <- enrichGO(gene = yeast_conserved, 
                                universe = yeast_all,
                                OrgDb = org.Sc.sgd.db,
                                ont = "ALL",
                                pAdjustMethod = "fdr",
                                pvalueCutoff  = 0.01,
                                qvalueCutoff  = 0.05)
head(yeast_conserved_ego)

```

# Gene Set Enrichment Analysis

human_conserved_gse <- gseGO(geneList = sort(human_conserved, decreasing = TRUE),
              OrgDb        = org.Hs.eg.db,
              ont          = "ALL",
              minGSSize    = 100,
              maxGSSize    = 500,
              pvalueCutoff = 0.05)
head(human_conserved_gse)

human_specific_gse <- gseGO(geneList = human_specific,
              OrgDb        = org.Hs.eg.db,
              ont          = "ALL",
              minGSSize    = 100,
              maxGSSize    = 500,
              pvalueCutoff = 0.05)
head(human_specific_gse)

yeast_conserved_gse <- gseGO(geneList = yeast_conserved,
              OrgDb        = org.Hs.eg.db,
              ont          = "ALL",
              minGSSize    = 100,
              maxGSSize    = 500,
              pvalueCutoff = 0.05,
              verbose      = FALSE)
head(human_specific_gse)

yeast_specific_gse <- gseGO(geneList = yeast_specific,
              OrgDb        = org.Hs.eg.db,
              ont          = "ALL",
              minGSSize    = 100,
              maxGSSize    = 500,
              pvalueCutoff = 0.05,
              verbose      = FALSE)
head(human_specific_gse)









head(human_specific_ego)

```{r}
dotplot(human_specific_ego, showCategory=30)+
scale_y_discrete(labels=function(x) str_wrap(x, width=30))+xlim(0, 0.15)
```

```{r}
dotplot(human_conserved_ego, showCategory=30)+
scale_y_discrete(labels=function(x) str_wrap(x, width=30))+
                 xlim(0, 0.15)
```

```{r}
dotplot(human_conserved_ego, showCategory=30)+
scale_y_discrete(labels=function(x) str_wrap(x, width=30))+xlim(0, 0.15)
```


```{r}
p <- dotplot(human_specific_ego, showCategory=30)+scale_y_discrete(labels=function(x) str_wrap(x, width=30))+xlim(0, 0.15)
```


# https://zhuanlan.zhihu.com/p/133342400

goplot(human_specific_ego)


